### 2013-05-30 trunk/papers/bprheo_r/bprheo.tex
Update paper bprheo_r 30 May
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1992 40876441-3496-0410-a613-a2fca35b2ae2

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage{mhchem}
\usepackage{times,mathptmx}
%\usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\newcommand{\e}[1]{\times10^{#1}}
\newcommand{\gd}{\dot{\gamma}}
\newcommand{\com}[1]{{\bf {#1}}}

@@

The time evolution of the fluid density and velocity are respectively governed
by the continuity equation
$\partial_t \rho = -\partial_\alpha(\rho v_\alpha)$, and
the following Navier-Stokes equation:
\begin{eqnarray}
\partial_t v_\alpha +\rho \,v_\beta \partial_\beta v_\alpha
&=& \partial_\beta \Pi_{\alpha \beta}+ \eta\, \partial_\beta [ \partial_\alpha v_\beta +\; \partial_\beta v_\alpha].
\label{NSE}
\end{eqnarray}
This emerges from the Chapman-Enskog expansion
of the lattice Boltzmann (LB) equations 
that we solve numerically. A further term $\eta(1+3\frac{\partial P_0}{\partial\rho} )\partial_\mu v_\mu \delta_{\alpha \beta}$ that formally appears
in this expansion is negligible under the slow flows considered here
for which the the fluid motion is almost incompressible~\cite{Denniston:2001}.
$\eta$ is an isotropic background viscosity which is set to $\eta=0.8333$ in LB units (these are discussed below, see~\cite{Henrich:2011a,Henrich:2010b}).
The thermodynamic stress tensor reads explicitly
\begin{eqnarray}
\Pi_{\alpha \beta}&=&P_0 \delta_{\alpha\beta}
-\xi H_{\alpha \gamma}\left(Q_{\gamma \beta} +\frac{1}{3} \delta_{\gamma \beta}\right)\nonumber\\
&-&\xi \left(Q_{\alpha \gamma} +\frac{1}{3} \delta_{\alpha \gamma}\right) H_{\gamma \beta} + Q_{\alpha \gamma}H_{\gamma \beta}-H_{\alpha \gamma} Q_{\gamma \beta} \nonumber\\
&+&2 \xi  \left(Q_{\alpha \beta} +\frac{1}{3} \delta_{\alpha \beta}\right) Q_{\gamma \nu} H_{\gamma \nu}
- \partial_\alpha Q_{\gamma \nu} \frac{\delta{\cal F}}{\delta \partial_{\beta} Q_{\gamma \nu}}\nonumber\\
\label{Pi}
\end{eqnarray}
and is responsible for strong non-Newtonian flow effects.
In the isotropic state ${\bf Q}\equiv 0$ and Eq.\ref{Pi} reduces to the
scalar pressure as would appear in Eq.~\ref{NSE} for a Newtonian fluid.

We next define a 
dimensionless number that describes the deformation
of the director field under flow. This so-called Ericksen number
is given by 
\begin{equation}
Er=\frac{\eta v l}{K}
\end{equation}
with $\eta$ and $K$ defined previously, and 
$v$ and $l$ a typical velocity and length scale. 
In the present work $l=p_0/2$ was used as this is the approximate size of
the BP unit cell. Likewise, $v$ was taken to be the velocity difference
across one unit cell, i.e. $v=\dot{\gamma} p_0/2$.

@@

We start our discussion with BPII as its flow behaviour is somewhat simpler 
than that of BPI. BPII has simple cubic symmetry and the disclination lines 
intersect and form a characteristic network of nodes.
Ahead of the more detailed discussion we provide first a general overview of the 
flow behaviour at all applied shear rates.
Fig. \ref{bp2-rheo} shows the ratio between the apparent viscosity, 
defined as 
$\eta_{app}=\langle \Pi_{xy} \rangle/\gd$, and $\eta$.
A numerical value of $\eta_{app}/\eta=1$ corresponds to a fully Newtonian flow,
without any additional contribution from the liquid crystal.
The top picture shows the data over time, whereas the graph at the bottom gives 
the same data versus accumulated strain.
For all but the highest flow rates $\eta_{app}$ oscillates sinusoidally, which
is because of the periodic breakup and reconnecting of the network in shear flow. 
We refer to this regime as BPII-1. As noted in the Appendix, the
absence at very low shear rate of a permeation mode is due to our
choice of boundary conditions.
%{We note that permeation flows, which would
%{\em not} lead to oscillatory response, are effectively disallowed by the combination
%of the geometry and boundary condition we consider. This is
%because the periodic boundary conditions impose macroscopic distortion
%of the network, and are effective analogous to infinitely distant
%but anchored wall along the $xy$ plane.
%This means that  our results are effectively valid for sheared bulk 
%BPs which are anchored at the walls. Furthermore, permeation flows are 
%only restricted to very slow flows, and are unstable for intermediate 
%and high flows, where the response of the network depends less on
%the details of the boundary conditions used at 
%the wall~\cite{Marenduzzo:2006a,Marenduzzo:2006b}.}

@@

\begin{figure}[htpb]
\center
\includegraphics[width=0.35\textwidth]{disc-160k_run902.png}
\includegraphics[width=0.35\textwidth]{disc-164k_run902.png}
\includegraphics[width=0.35\textwidth]{disc-165k_run902.png}
\caption{Disclination network of BPII in shear flow: 
The pictures show a typical sequence of snapshots in the steady state 
at $\gd=1.56\e{-4}$ and time steps $t=1.60, 1.64,1.65\e{5}$. The velocity 
gradient is oriented along the vertical direction (y), whereas the 
horizontal direction (x) is the flow direction. Lees-Edwards boundary 
conditions have been imposed in such a way that the network moves to the 
right in the upper half and to the left in the lower half of the picture.}
\label{bp2-med}
\end{figure}

\begin{figure*}[htpb]
\includegraphics[width=0.495\textwidth]{v_yz-v_z-160k_run902.png}
\includegraphics[width=0.495\textwidth]{v_yz-v_z-160k_run903.png}
\caption{Velocity patterns and disclination network in BPII for positive (left) and negative (right) helicity of the 
underlying cholesteric helix: The pictures show velocity vectors $(0,v_y,v_z)$.
The view is along the x-direction. This means the velocity ${\mathbf v}$ 
has been projected onto a plane perpendicular to the flow direction. 
The vertical and horizontal direction are the gradient and vorticity direction, respectively.
The colour code gives the magnitude and sign of the component in vorticity direction.
The snapshot shows a typical frame during a periodically recurring sequence.
The network on the left with right-handed helicity ($q_0>0$ in Eq.~\ref{FE}) travels rightwards, whereas the one one the right,
with reversed helicity, moves leftward. 
The periodicity of the motion along the vorticity direction is six times longer than the time 
it takes the network to reconnect along the flow direction.}
\label{bp2-velo}
\end{figure*}

@@

If the flow rate exceeds a certain critical value BPII does not undergo the 
homogeneous deformation described above and adopts another mode of flow. 
Fig. \ref{bp2-high} shows a sequence of cuts through the director 
field at high shear rate. The entire blue phase network has broken up 
into a simple cholesteric helix and flows as a travelling 
helical wave with the helical axis oriented along the vorticity direction.
The state is translationally invariant in the flow and gradient directions.
It is the preferred mode of flow of a standard cholesteric phase
in vorticity mode at low Ericksen numbers. This is followed by
the uncoiling transition to a nematic, flow-aligned state at even 
higher shear rates ~\cite{Rey:1996a, Rey:1996b}.

In our scenario the BP to cholesteric transition occurs for shear rates $\gd\simeq 4.68\e{-4}$, which
corresponds to Ericksen numbers of ${\it Er}\simeq4$, based on our
parameters for BPII ($K=0.02, \eta=0.666$, and $p_0/2=16$;
see Table \ref{tab1} in the Appendix).

\begin{figure}[htpb]
\includegraphics[width=0.495\textwidth]{dir+y-250k_run949.png}
\includegraphics[width=0.495\textwidth]{dir+y-253k_run949.png}
\includegraphics[width=0.495\textwidth]{dir+y-255k_run949.png}
\includegraphics[width=0.495\textwidth]{dir+y-257k_run949.png}
\caption{Director field of BPII at high shear rate: The images show snapshots at time steps 
$t=2.50, 2.53,2.55, 2.57\e{5}$ (from top to bottom) with flow into/out of the page. The colour code gives the alignment of the director field in the flow direction (x) with red fully aligned and blue out of plane. 
The configuration is a helical wave that travels along the direction of vorticity.
It is translationally invariant along the gradient and flow direction.}
\label{bp2-high}
\end{figure}

@@

\begin{table*}[htpb]
\begin{tabular}{|c||c|| c || c || c |c |c||c| c| c||c| c| c|}
\hline
& $\dot{\gamma}$ & ${\it Er}$ & $q_0$ & $\bar{v}_{x,min}$ & $\bar{v}_{x,max}$ & $\bar{v}_{x,std}$ & $\bar{v}_{y,min}$ & $\bar{v}_{y,max}$ & $\bar{v}_{y,std}$ & $\bar{v}_{z,min}$ & $\bar{v}_{z,max}$ & $\bar{v}_{z,std}$ \\
\hline
BPI & & & & $\times 10^5$\\
\hline
BPI-1 & 0.244 & 0.04& 0.1388 &-15.79 &15.57 &1.04 &-0.89 &0.91 &0.95 &-1.59 &1.19 &1.27 \\
BPI-1 & 0.488 & 0.08 & 0.1388 &-31.11 &31.25 &1.31 &-0.93 &0.98 &1.28 &-1.62 &1.10 &1.40 \\
BPI-1 & 0.976 & 0.17 & 0.1388 &-62.24 &62.37 &2.51 &-1.31 &1.25 &2.68 &-1.24 &0.87 &2.65 \\
BPI-1 & 1.95 & 0.33 & 0.1388 &-124.65 &124.82 &3.62&  -2.49 &2.50 &4.51 &-1.89 & 1.62 &3.51 \\
\hline
BPI-2 & 3.91 & 0.67 & 0.1388 &-248.69 &248.74 &3.90&  -3.31 &3.35 &4.21 &-2.56 & 2.88 &4.39 \\
BPI-2 & 7.81 & 1.33 & 0.1388 &-497.22 &496.16 &4.46 &-6.49 &6.56 &7.99 &-5.31 & 7.46 &6.81 \\ 
BPI-2 & 15.63 & 2.67 & 0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-2.87} & \bf{3.57} &10.54 \\
BPI-2 & 15.63 & 2.67 & -0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-3.57} & \bf{2.87} &10.54 \\
BPI-2 & 31.25 &5.33 & 0.1388 & -1988.36 &1986.71 &16.85 &-4.08 &4.46 &15.94 &-11.37 & 12.16 &19.38\\
BPI-2 & 46.87 & 8.00 & 0.1388 & -3025.46 & 3003.05 &21.43 & -56.96 & 56.44  & 18.75 & -12.65 & 82.97  & 27.96\\
\hline
BPI-3 & 62.50 & 10.67& 0.1388 & -4039.41 &3995.3  & 20.57 & -62.63 & 62.13 & 24.68 &-73.52 & 110.76 & 33.26 \\
BPI-3 &78.13 &13.33 & 0.1388 & -4968.11 &4973.75 &20.89 &-60.61 &58.75 &23.66 &-84.93 &116.61 &34.75 \\
\hline
CHG & 93.75 &16.00 & 0.1388 & -5955.12 &5948.84 & 0.71 & -0.002 & 0.002 & -  & -16.45 & 16.03 &0.62 \\
CHG & 125.0 & 21.33& 0.1388 & -7934.97 & 7935.41 & 0.36 & -0.005 & 0.005 & - &-22.73 & 21.12 & 0.07\\
\hline
FAN & 187.5 & 32.00& 0.1388 &-11906.4  &119064 &0.36 &- &- &- &-0.68 & 0.38 & 0.05\\
\hline

BPII  & & & & $\times 10^5$ \\
\hline
BPII-1 & 0.244 &0.02 & 0.1963 &-7.75 &7.70 &0.13 &-0.17 &0.17 &0.13 &-0.24 &0.23 &0.19 \\
BPII-1 & 0.488 &0.04 & 0.1963 &-15.50 &15.40 &0.19 &-0.32 &0.30 &0.21 &-0.43 &0.42 &0.29 \\
BPII-1 & 0.976 &0.08 & 0.1963 &-31.01 &30.80 &0.33 &-0.60 &0.58 &0.41 &-0.85 &0.79 &0.47 \\
BPII-1 & 1.95 &0.17  & 0.1963 &-62.04  &61.60 & 0.97 & -1.09 &1.07 & 0.76 & -1.64 & 1.55 & 0.81\\
BPII-1 &3.91 & 0.33& 0.1963 &-123.93 &123.18 & 1.76 &-1.66 &1.70 & 1.45 &-3.09& 2.73 &1.47\\
BPII-1 &7.81 &0.67 & 0.1963  &-247.67 &246.45 & 3.20 &-2.62 &2.71 & 2.67 &-5.78 & 4.77 &2.74\\
BPII-1 &15.63 & 1.33& 0.1963 &-494.85 &493.09 & 5.64 &-3.13 &3.31 &4.24 &\bf{-10.00} & \bf{7.66} &4.33\\
BPII-1 & 15.63 & 1.33& -0.1963&-494.85 &493.09 & 5.64 & -3.13 &3.31 &4.24 &\bf{-7.66} & \bf{10.00} &4.33\\
BPII-1 & 31.25 &2.67 & 0.1963 &-988.73 &985.93 &8.96  &-1.79 &1.82 &5.86 &-14.39 & 11.04 &6.35\\
\hline
BPII-2 & 46.87 &4.00 & 0.1388 & -1476.75 & 1476.84 &1.69 &-0.35  &0.35  & 0.17 &-0.23 &0.23  & 0.22\\
BPII-2 & 62.50 & 5.34& 0.1963 & -1969.41  & 1969.41 & 3.07 & -1.20 & 1.20 & 0.38 &-0.96 & 1.48 &0.38 \\
\hline
CHG & 78.13 & 6.66 &  0.1388 &-2458.60 & 2458.61  &0.37 &- &- &- &-18.54 &16.94 &0.32 \\
CHG & 93.75 &8.00 & 0.1388 &-2950.2  &2950.2 &0.50 &- &- &- &-22.69 & 19.72 & 0.04\\
\hline
FAN & 125.0 &10.67 & 0.1388 &-3937.31  & 3937.32 &0.28 &-  &-  &-  &-1.79 &1.15  &0.14 \\
\hline
\end{tabular}
\caption{Minima, maxima and standard deviation of time-averaged velocity components 
for BPI ($\tau=-0.5, \kappa=1.0$) and BPII ($\tau=-0.5, \kappa=2.0$) in steady 
shear flow. All velocity values are given in $10^{-5}$ lattice units. The transient dynamics 
has not been included in the averages. The regimes comprise the formation
of an amorphous network (BPI-1), periodically recurring conformations (BPI-2 and BPII-1), 
two-dimensional double twist rolls (BPI-3), a one-dimensional travelling helical wave (BPII-2), 
a cholesteric helix oriented along the gradient direction (CHG), 
and a flow-aligned nematic state (FAN).
(Last six columns refer to the secondary flow.)}
\label{tab1}
\end{table*}

>>>>

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage{mhchem}
\usepackage{times,mathptmx}
%\usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance} 
\usepackage{color}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\newcommand{\e}[1]{\times10^{#1}}
\newcommand{\gd}{\dot{\gamma}}
\newcommand{\com}[1]{{\bf {#1}}}
\newcommand{\rev}[1]{{\textcolor{red}{#1}}}

@@

The time evolution of the fluid density and velocity are respectively governed
by the continuity equation
$\partial_t \rho = -\partial_\alpha(\rho v_\alpha)$, and
the following Navier-Stokes equation:
\begin{eqnarray}
\partial_t v_\alpha +\rho \,v_\beta \partial_\beta v_\alpha
&=& \partial_\beta \Pi_{\alpha \beta}+ \eta\, \partial_\beta [ \partial_\alpha v_\beta +\; \partial_\beta v_\alpha].
\label{NSE}
\end{eqnarray}
This emerges from the Chapman-Enskog expansion
of the lattice Boltzmann (LB) equations 
that we solve numerically. A further term $\eta(1+3\frac{\partial P_0}{\partial\rho} )\partial_\mu v_\mu \delta_{\alpha \beta}$ that formally appears
in this expansion is negligible under the slow flows considered here
for which the the fluid motion is almost incompressible~\cite{Denniston:2001}.
$\eta$ is an isotropic background viscosity which is set to $\eta=0.6666$ in LB units (these are discussed below, see~\cite{Henrich:2011a,Henrich:2010b}).
The thermodynamic stress tensor reads explicitly
\begin{eqnarray}
\Pi_{\alpha \beta}&=&P_0 \delta_{\alpha\beta}
-\xi H_{\alpha \gamma}\left(Q_{\gamma \beta} +\frac{1}{3} \delta_{\gamma \beta}\right)\nonumber\\
&-&\xi \left(Q_{\alpha \gamma} +\frac{1}{3} \delta_{\alpha \gamma}\right) H_{\gamma \beta} + Q_{\alpha \gamma}H_{\gamma \beta}-H_{\alpha \gamma} Q_{\gamma \beta} \nonumber\\
&+&2 \xi  \left(Q_{\alpha \beta} +\frac{1}{3} \delta_{\alpha \beta}\right) Q_{\gamma \nu} H_{\gamma \nu}
- \partial_\alpha Q_{\gamma \nu} \frac{\delta{\cal F}}{\delta \partial_{\beta} Q_{\gamma \nu}}\nonumber\\
\label{Pi}
\end{eqnarray}
and is responsible for strong non-Newtonian flow effects.
In the isotropic state ${\bf Q}\equiv 0$ and Eq.\ref{Pi} reduces to the
scalar pressure as would appear in Eq.~\ref{NSE} for a Newtonian fluid.

We next define a 
dimensionless number that describes the deformation
of the director field under flow. This so-called Ericksen number
is given by 
\begin{equation}
Er=\frac{\eta v l}{K}
\end{equation}
with $\eta$ and $K$ defined previously, and 
$v$ and $l$ a typical velocity and length scale. 
In the present work $l=p_0/2=\pi/q_0$ was used as this is the approximate size of
the BP unit cell. Likewise, $v$ was taken to be the velocity difference
across one unit cell, i.e. $v=\dot{\gamma} l$. The elastic constant was taken as $K=0.02$ (BPII) and $K=0.04$ (BPI), respectively.

@@

We start our discussion with BPII as its flow behaviour is somewhat simpler 
than that of BPI. BPII has simple cubic symmetry and the disclination lines 
intersect and form a characteristic network of nodes.
Ahead of the more detailed discussion we provide first a general overview of the 
flow behaviour at all applied shear rates.
Fig. \ref{bp2-rheo} shows the ratio between the apparent viscosity, 
defined as 
$\eta_{app}=\langle \Pi_{xy} \rangle/\gd +\eta$, and $\eta$.
A numerical value of $\eta_{app}/\eta=1$ corresponds to a fully Newtonian flow,
without any additional contribution from the liquid crystal.
The top picture shows the data over time, whereas the graph at the bottom gives 
the same data versus accumulated strain.
For all but the highest flow rates $\eta_{app}$ oscillates sinusoidally, which
is because of the periodic breakup and reconnecting of the network in shear flow. 
We refer to this regime as BPII-1. As noted in the Appendix, the
absence at very low shear rate of a permeation mode is due to our
choice of boundary conditions.
%{We note that permeation flows, which would
%{\em not} lead to oscillatory response, are effectively disallowed by the combination
%of the geometry and boundary condition we consider. This is
%because the periodic boundary conditions impose macroscopic distortion
%of the network, and are effective analogous to infinitely distant
%but anchored wall along the $xy$ plane.
%This means that  our results are effectively valid for sheared bulk 
%BPs which are anchored at the walls. Furthermore, permeation flows are 
%only restricted to very slow flows, and are unstable for intermediate 
%and high flows, where the response of the network depends less on
%the details of the boundary conditions used at 
%the wall~\cite{Marenduzzo:2006a,Marenduzzo:2006b}.}

@@

\begin{figure}[htpb]
\center
\includegraphics[width=0.35\textwidth]{disc-160k_run902r.png}
\includegraphics[width=0.35\textwidth]{disc-164k_run902r.png}
\includegraphics[width=0.35\textwidth]{disc-165k_run902r.png}
\caption{Disclination network of BPII in shear flow: 
The pictures show a typical sequence of snapshots in the steady state 
at $\gd=1.56\e{-4}$ and time steps $t=1.60, 1.64,1.65\e{5}$. The velocity 
gradient is oriented along the vertical direction (y), whereas the 
horizontal direction (x) is the flow direction. Lees-Edwards boundary 
conditions have been imposed in such a way that the network moves to the 
right in the upper half and to the left in the lower half of the picture.}
\label{bp2-med}
\end{figure}

\begin{figure*}[htpb]
\includegraphics[width=0.495\textwidth]{v_yz-v_z-160k_run902r.png}
\includegraphics[width=0.495\textwidth]{v_yz-v_z-160k_run903r.png}
\caption{Velocity patterns and disclination network in BPII for positive (left) and negative (right) helicity of the 
underlying cholesteric helix: The pictures show velocity vectors $(0,v_y,v_z)$.
The view is along the x-direction. This means the velocity ${\mathbf v}$ 
has been projected onto a plane perpendicular to the flow direction. 
The vertical and horizontal direction are the gradient and vorticity direction, respectively.
The colour code gives the magnitude and sign of the component in vorticity direction.
The snapshot shows a typical frame during a periodically recurring sequence.
The network on the left with right-handed helicity ($q_0>0$ in Eq.~\ref{FE}) travels rightwards, whereas the one one the right,
with reversed helicity, moves leftward. 
The periodicity of the motion along the vorticity direction is six times longer than the time 
it takes the network to reconnect along the flow direction.}
\label{bp2-velo}
\end{figure*}

@@

%If the flow rate exceeds a certain critical value BPII does not undergo the 
%homogeneous deformation described above and adopts another mode of flow. 
%Fig. \ref{bp2-high} shows a sequence of cuts through the director 
%field at high shear rate. The entire blue phase network has broken up 
%into a simple cholesteric helix and flows as a travelling 
%helical wave with the helical axis oriented along the vorticity direction.
%The state is translationally invariant in the flow and gradient directions.
%It is the preferred mode of flow of a standard cholesteric phase
%in vorticity mode at low Ericksen numbers. This is followed by
%the uncoiling transition to a nematic, flow-aligned state at even 
%higher shear rates ~\cite{Rey:1996a, Rey:1996b}.

%In our scenario the BP to cholesteric transition occurs for shear rates $\gd\simeq 4.68\e{-4}$, which
%corresponds to Ericksen numbers of ${\it Er}\simeq4$, based on our
%parameters for BPII ($K=0.02, \eta=0.666$, and $p_0/2=16$;
%see Table \ref{tab1} in the Appendix).

%\begin{figure}[htpb]
%\includegraphics[width=0.495\textwidth]{dir+y-250k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-253k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-255k_run949.png}
%\includegraphics[width=0.495\textwidth]{dir+y-257k_run949.png}
%\caption{Director field of BPII at high shear rate: The images show snapshots at time steps 
%$t=2.50, 2.53,2.55, 2.57\e{5}$ (from top to bottom) with flow into/out of the page. The colour code gives the alignment of the director field in the flow direction (x) with red fully aligned and blue out of plane. 
%The configuration is a helical wave that travels along the direction of vorticity.
%It is translationally invariant along the gradient and flow direction.}
%\label{bp2-high}
%\end{figure}

@@

\begin{table*}[htpb]
\begin{tabular}{|c||c|| c || c || c |c |c||c| c| c||c| c| c|}
\hline
& $\dot{\gamma}$ & ${\it Er}$ & $q_0$ & $\bar{v}_{x,min}$ & $\bar{v}_{x,max}$ & $\bar{v}_{x,std}$ & $\bar{v}_{y,min}$ & $\bar{v}_{y,max}$ & $\bar{v}_{y,std}$ & $\bar{v}_{z,min}$ & $\bar{v}_{z,max}$ & $\bar{v}_{z,std}$ \\
\hline
BPI & & & & $\times 10^5$\\
\hline
BPI-1 &0.24 &0.02 & 0.1388 & & & & & & & & & \\
BPI-1 &0.49 &0.04 & 0.1388 & & & & & & & & & \\
BPI-1 &0.98 &0.08 & 0.1388 & & & & & & & & & \\
BPI-1 &1.95 &0.17 & 0.1388 & & & & & & & & & \\
%BPI-1 & 0.244 & 0.04& 0.1388 &-15.79 &15.57 &1.04 &-0.89 &0.91 &0.95 &-1.59 &1.19 &1.27 \\
%BPI-1 & 0.488 & 0.08 & 0.1388 &-31.11 &31.25 &1.31 &-0.93 &0.98 &1.28 &-1.62 &1.10 &1.40 \\
%BPI-1 & 0.976 & 0.17 & 0.1388 &-62.24 &62.37 &2.51 &-1.31 &1.25 &2.68 &-1.24 &0.87 &2.65 \\
%BPI-1 & 1.95 & 0.33 & 0.1388 &-124.65 &124.82 &3.62&  -2.49 &2.50 &4.51 &-1.89 & 1.62 &3.51 \\
\hline
BPI-2 &3.91 &0.33 & 0.1388 & & & & & & & & & \\
BPI-2 &7.81 &0.67 & 0.1388 & & & & & & & & & \\
BPI-2 &15.63 &1.33 & 0.1388 & & & & & & & & & \\
BPI-2 &15.63 &1.33 & -0.1388 & & & & & & & & & \\
BPI-2 &23.44 &2.00 & 0.1388 & & & & & & & & & \\
%BPI-2 & 7.81 & 1.33 & 0.1388 &-497.22 &496.16 &4.46 &-6.49 &6.56 &7.99 &-5.31 & 7.46 &6.81 \\ 
%BPI-2 & 15.63 & 2.67 & 0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-2.87} & \bf{3.57} &10.54 \\
%BPI-2 & 15.63 & 2.67 & -0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-3.57} & \bf{2.87} &10.54 \\
%BPI-2 & 31.25 &5.33 & 0.1388 & -1988.36 &1986.71 &16.85 &-4.08 &4.46 &15.94 &-11.37 & 12.16 &19.38\\
%BPI-2 & 46.87 & 8.00 & 0.1388 & -3025.46 & 3003.05 &21.43 & -56.96 & 56.44  & 18.75 & -12.65 & 82.97  & 27.96\\
\hline
BPI-3 &31.25 &2.66 & 0.1388 & & & & & & & & & \\
BPI-3 &46.87 &4.00 & 0.1388 & & & & & & & & & \\
BPI-3 &54.69 &4.67 & 0.1388 & & & & & & & & & \\
BPI-3 &62.50 &5.33 & 0.1388 & & & & & & & & & \\
BPI-3 &78.13 &6.01 & 0.1388 & & & & & & & & & \\
%BPI-3 &78.13 &13.33 & 0.1388 & -4968.11 &4973.75 &20.89 &-60.61 &58.75 &23.66 &-84.93 &116.61 &34.75 \\
\hline
GJT (BPI-4) &93.75 &8.00 & 0.1388 & & & & & & & & & \\
GJT (BPI-4) &125.0 &10.66 & 0.1388 & & & & & & & & & \\
GJT (BPI-4) &187.5 &16.00 & 0.1388 & & & & & & & & & \\
%GJT (BPI-4)& 125.0 & 21.33& 0.1388 & -7934.97 & 7935.41 & 0.36 & -0.005 & 0.005 & - &-22.73 & 21.12 & 0.07\\
\hline
FAN & 250.0 &21.33 & 0.1388 & & & & & & & & & \\
FAN & 375.0 &32.00 & 0.1388 & & & & & & & & & \\
%FAN & 187.5 & 32.00& 0.1388 &-11906.4  &119064 &0.36 &- &- &- &-0.68 & 0.38 & 0.05\\
\hline

BPII  & & & & $\times 10^5$ \\
\hline
BPII-1 &0.24 &0.02 & 0.1963 & & & & & & & & & \\
BPII-1 &0.49 &0.04 & 0.1963 & & & & & & & & & \\
BPII-1 &0.98 &0.08 & 0.1963 & & & & & & & & & \\
BPII-1 &1.95 &0.17 & 0.1963 & & & & & & & & & \\
BPII-1 &3.91 &0.33 & 0.1963 & & & & & & & & & \\
BPII-1 &7.81 &0.67 & 0.1963 & & & & & & & & & \\
BPII-1 &15.63 &1.33 & 0.1963 & & & & & & & & & \\
BPII-1 &15.63 &1.33 & -0.1963 & & & & & & & & & \\
BPII-1 &31.25 &2.66 & 0.1963 & & & & & & & & & \\
BPII-1 &39.06 &3.33 & 0.1963 & & & & & & & & & \\
%BPII-1 & 0.244 &0.02 & 0.1963 &-7.75 &7.70 &0.13 &-0.17 &0.17 &0.13 &-0.24 &0.23 &0.19 \\
%BPII-1 & 0.488 &0.04 & 0.1963 &-15.50 &15.40 &0.19 &-0.32 &0.30 &0.21 &-0.43 &0.42 &0.29 \\
%BPII-1 & 0.976 &0.08 & 0.1963 &-31.01 &30.80 &0.33 &-0.60 &0.58 &0.41 &-0.85 &0.79 &0.47 \\
%BPII-1 & 1.95 &0.17  & 0.1963 &-62.04  &61.60 & 0.97 & -1.09 &1.07 & 0.76 & -1.64 & 1.55 & 0.81\\
%BPII-1 &3.91 & 0.33& 0.1963 &-123.93 &123.18 & 1.76 &-1.66 &1.70 & 1.45 &-3.09& 2.73 &1.47\\
%BPII-1 &7.81 &0.67 & 0.1963  &-247.67 &246.45 & 3.20 &-2.62 &2.71 & 2.67 &-5.78 & 4.77 &2.74\\
%BPII-1 &15.63 & 1.33& 0.1963 &-494.85 &493.09 & 5.64 &-3.13 &3.31 &4.24 &\bf{-10.00} & \bf{7.66} &4.33\\
%BPII-1 & 15.63 & 1.33& -0.1963&-494.85 &493.09 & 5.64 & -3.13 &3.31 &4.24 &\bf{-7.66} & \bf{10.00} &4.33\\
%BPII-1 & 31.25 &2.67 & 0.1963 &-988.73 &985.93 &8.96  &-1.79 &1.82 &5.86 &-14.39 & 11.04 &6.35\\
\hline
GJT (BPII-2)&46.87 &4.00 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&54.69 &4.67 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&62.5 &5.33 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&78.13 &6.01 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&93.75 &8.00 & 0.1963 & & & & & & & & & \\
GJT (BPII-2)&125.0 &10.66 & 0.1963 & & & & & & & & & \\
%GJT (BPII-2)& 62.50 & 5.34& 0.1963 & -1969.41  & 1969.41 & 3.07 & -1.20 & 1.20 & 0.38 &-0.96 & 1.48 &0.38 \\
%GJT (BPII-2) & 78.13 & 6.66 &  0.1388 &-2458.60 & 2458.61  &0.37 &- &- &- &-18.54 &16.94 &0.32 \\
%GJT (BPII-2)& 93.75 &8.00 & 0.1388 &-2950.2  &2950.2 &0.50 &- &- &- &-22.69 & 19.72 & 0.04\\
\hline
FAN &187.5 &16.00 & 0.1963 &  & & &  &  &  & & & \\
FAN &250.0 &21.33 & 0.1963 &  & & &  &  &  & & & \\
%FAN & 125.0 &10.67 & 0.1388 &-3937.31  & 3937.32 &0.28 &-  &-  &-  &-1.79 &1.15  &0.14 \\
\hline
\end{tabular}
\caption{Minima, maxima and standard deviation of time-averaged velocity components 
for BPI ($\tau=-0.5, \kappa=1.0$) and BPII ($\tau=-0.5, \kappa=2.0$) in steady 
shear flow. All velocity values are given in $10^{-5}$ lattice units. The transient dynamics 
has not been included in the averages. The regimes comprise the formation
of an amorphous network (BPI-1), periodically recurring conformations (BPI-2 and BPII-1), 
two-dimensional double twist rolls (BPI-3), a one-dimensional travelling helical wave (BPII-2), 
a cholesteric helix oriented along the gradient direction (CHG), 
and a flow-aligned nematic state (FAN).
(Last six columns refer to the secondary flow.)}
\label{tab1}
\end{table*}
